BoostEM

### 2014-05-07 paper/paper.tex
soefkwelfjwe
work on my sections

@@

\subsection{Methodology}
STEVE
\subsection{Results}

>>>>

We evaluated the performance of our algorithm on four data sets from the UCI Machine Learning Repository: Breast Cancer Wisconsin (Diagnostic), which classifies digitized images of breast mass as benign or malignant; Parkinsons, which classifies biomedical voice measurements from patients as healthy or Parkinson's; Banknote Authentication, which classifies pictures of currency as genuine or foraged; and Vertebral Column, which classifies biomedical data from patients as either normal or abnormal vertebral column. Each dataset is for a binary classification task, and each attribute is real-valued. For each dataset, the number of attributes ranges from 5 to 32 and the number of instances ranges from 197 to 1372.

@@

We used five other algorithms for comparison to BoostEM to evaluate its performance. The following lists the algorithms' abbreviations as used in the graphs and discussion and describes them.

\begin{enumerate}
\item \textbf{BoostEM}: our implementation of the BoostEM algorithm
\item \textbf{FullBoost}: applying the AdaBoost algorithm to the fully labeled dataset
\item \textbf{justBoost} applying the AdaBoost algorithm to the fraction of the labeled dataset
\item \textbf{justEM} applying Expectation Maximization to the fraction of the labeled dataset
\item \textbf{full\{Algorithm A\}} applying A to the fully labeled dataset without Boosting or EM
\item \textbf{just\{Algorithm A\}} applying A to the fraction of the labeled dataset without Boosting or EM
\end{enumerate}

\subsection{Methodology}

We evaluated the aforementioned algorithms manipulating the following parameters.

\begin{enumerate}
\item \textbf{Dataset}: Breast Cancer Wisconsin (Diagnostic), Parkinsons, Banknote Authentication, Vertebral Column
\item \textbf{Learner}: ID3 Decision Tree, Naive Bayes
\item \textbf{Fraction of Labeled Instances} 5\%, 20\%
\end{enumerate}

For each combination of these parameters, we averaged the resulting accuracies of five 10-fold cross validation runs.

\subsection{Results}
